\chapter{Conclusions}

Please also focus on this chapter! I know that sometimes while writing a document, conclusions are the last thing to write, but remember that they are also the last thing to read and might change the reader's overall perspective of the document. I would want you to answer to the following questions and, why not, even some added by yourself. 

\begin{itemize}
  \item \textbf{What did we learn?}
  
  (e.g.) During this semester, we learned X and Y. 
  
  \item \textbf{What mark would I give to me? How much did I contribute to the teamwork (project, application, presentation)? What mark do I think my colleagues deserve?}
  
  (e.g.) If it were up to me, I would give myself \textbf{...}, because even if the project is pretty good, I did (not) help as much as my colleagues. (e.g.) I consider 20\% of the final project is because of me. Also, I want to add that we did (not) indeed work as a team and I think all of us should get the same mark. (or not) 
  
  \textit{Remember each one of you will have to upload the documentation on Campus, but the answers to these questions have to be unique. (this one in particular).}

  \item \textbf{What was hard, what did we enjoy, what did we hate, what did we like and dislike about the CO project?}
  
  \item \textbf{How would you change (improve) the project meetings for the next generation of students?}
  
  I will definitely take into consideration your feedback and I will consider applying your suggestions as I did with most of the ideas gained last year.
  
\end{itemize}